Dynamics of Anthropomorphism in Human-Robot Interaction

### 2014-04-07 paper.tex
abstract, now: really robust draft :)

\textit{Anthropomorphism} -- the people's tendency to perceive human-like
characteristics in non-human agents -- is a phenomenon that is most often
studied from the sole perspective of the human-like \emph{design} of robots.

By building upon experimental results from several studies, a comprehensive
synthesis of the literature, as well as insights from social psychology,
cognitive science, and neuroscience, this article proposes to extend our current
understanding of anthropomorphism into a \textbf{formal model} that defines a
\textbf{clear terminology}, accounts for the \textbf{non-monotonic dynamics} of
the phenomenon, and relate the observed \emph{effects} of anthropomorphism to
their \textbf{underlying cognitive precursors}.

We also examine the \textbf{factors} that determine anthropomorphism (the
design of the non-human agent, the individual psychological determinants of the
human user and the context of use) and we discuss several \textbf{episodes of
interaction} that influence the anthropomorphic projections on the robot, like
the \textbf{novelty effect}, the role of \textbf{familiarization} and the
impact of \textbf{disruptive behaviors}.

The article also discusses techniques and scenarios to measure anthropomorphism,
and we conclude with a few suggestions on how others can apply our model to
better describe our tendency to perceive human-like characteristics in non-human
agents.

>>>>

\textit{Anthropomorphism} -- people's tendency to perceive human-like
characteristics in non-human agents -- is a phenomenon that is often
studied from the sole perspective of the human-like \emph{design} of robots.

By building upon experimental results from several studies, a comprehensive
synthesis of literature, as well as insights from social psychology,
cognitive science, and neuroscience, this article proposes to extend our current
understanding of anthropomorphism. By doing so, we propose a \textbf{formal model} that defines a
\textbf{clear terminology} and accounts for the \textbf{non-monotonic dynamics} of
the phenomenon. We further relate the observed \emph{effects} of anthropomorphism to
their \textbf{underlying cognitive precursors}.

We examine several \textbf{factors} that determine anthropomorphism, namely the
design of the non-human agent, the individual psychological determinants of the
human user, and the context of use. Moreover, we discuss several \textbf{episodes of
interaction} that influence the anthropomorphic projections on the robot, like
the \textbf{novelty effect}, the role of \textbf{familiarization} and the
impact of \textbf{disruptive behaviors}.

Finally, the article also discusses techniques and scenarios to measure anthropomorphism,
and we conclude with a few suggestions on how others can apply our model to
better describe people's tendency to perceive human-like characteristics in non-human
agents.
